---
title: "Untitled"
author: "Haechan Jung"
date: "2024-12-22"
output: pdf_document
---
1. Data collection and preparation = {Data Collection / check Null & Outlier / 
                                      Data type transformation } = data preprocessing
                                      
2. Data overview = check data size, variables, data types. understand overall data

3. Data visualization = histogram/scatter plot/box plot. 
                        Check data distribution and characteristics
4. Descriptive statistics = mean / median / standard deviation => tendency & variability

5. Correlaiton analysis = relationships btw variables; check independencies

6. Pattern discovery = various perspectives to uncover patterns => new hypotheses.

7. Interpretation and sharing = interprets the result of EDA and share them with others
                                to guid the data analysis direction.


```{r message = FALSE, warning=FALSE}
library(alr4)
library(tidyverse)
library(readr)
library(dplyr)
library(dbplyr)
library(DBI)
library(RSQLite)
```
```{r message = FALSE, warning=FALSE}
view_history = read_csv("C:/Users/user/OneDrive/바탕 화면/프로젝트/youtube_view_history_data_analysis/youtube_view_history.csv")
summary(view_history)
view_history
```
```{r}
# check if there is a NULL
sum(is.na(view_history$video_link))
sum(is.na(view_history$video_title))
sum(is.na(view_history$channel_link))
sum(is.na(view_history$channel_name))
sum(is.na(view_history$viewing_time))
```
```{r}
# convert viewing_time to characters
view_history$viewing_time_str <- format(view_history$viewing_time, "%Y-%m-%d %H:%M:%S")
```


```{r}
conn = src_memdb()
conn_isolated = conn$con
copy_to(conn, view_history, overwrite = TRUE)
```
```{sql connection=conn_isolated}
WITH time_change AS
( -- Standard time zone modification
SELECT strftime('%s', '2024-08-16 10:20:00') AS Kra_to_US -- 2024/08/16 10:20 KST Korea -> USA
     , strftime('%s', '2024-12-14 16:30:00') AS US_to_Kra -- 2024/12/14 16:30 KST USA -> Korea
     , strftime('%s', '2024-11-03 16:00:00') AS dst       -- 2024/11/03 16:00 KST daylight saving time
),

view_history_adj AS
(
SELECT *,
       CASE
          WHEN viewing_time >= kra_to_US 
           AND viewing_time < dst THEN 
           strftime('%Y-%m-%d %H:%M:%S', viewing_time, '-14 hours')
          WHEN viewing_time >= dst
           AND viewing_time < US_to_Kra THEN 
           strftime('%Y-%m-%d %H:%M:%S', viewing_time, '-13 hours')
          ELSE viewing_time
       END AS viewing_time_adj
FROM view_history
  JOIN time_change
),
view_history_date AS
(
SELECT *
     , strftime('%Y', viewing_time) AS year_og
     , strftime('%m', viewing_time) AS month_og
     , strftime('%d', viewing_time) AS _date_og
     , CASE strftime('%w', viewing_time) 
          WHEN '0' THEN 'Sun'
          WHEN '1' THEN 'Mon'
          WHEN '2' THEN 'Tue'
          WHEN '3' THEN 'Wed'
          WHEN '4' THEN 'Thu'
          WHEN '5' THEN 'Fri'
          WHEN '6' THEN 'Sat'
       END AS day_og
     , strftime('%H', viewing_time) AS hour_og
     , strftime('%M', viewing_time) AS minute_og
     , strftime('%S', viewing_time) AS second_og
FROM view_history
)

SELECT *
FROM view_history_adj




```
```{r}
# most watched channels
df_group_channels = tbl(conn, sql("SELECT channel_name
                                        , COUNT(DISTINCT video_link) AS cnts
                                        , channel_link
                                   FROM view_history
                                   GROUP BY channel_link
                                   ORDER BY cnts DESC"))

# excluding posts and music videos; only video view history
df_without_posts_n_musics = tbl(conn, sql("SELECT *
                                           FROM view_history
                                           WHERE video_link NOT LIKE '%music.youtube.com%' 
                                             AND video_link NOT LIKE '%youtube.com\\post%'"))

# make csv files
write.csv(df_group_channels, "C:/Users/user/OneDrive/바탕 화면/프로젝트/youtube_view_history_data_analysis/viewhistory_BY_Channels.csv")
write.csv(df_without_posts_n_musics, "C:/Users/user/OneDrive/바탕 화면/프로젝트/youtube_view_history_data_analysis/viewhistory_only_videos.csv")
```

```{sql connection=conn_isolated}
-- all_cnts = 전체 동영상 수
-- all_distinct_cnts = 시청한 개별적인 동영상 수
SELECT COUNT(video_link) AS all_cnts
    ,  COUNT(DISTINCT video_link) as all_distinct_cnts
FROM view_history
```
```{sql connection = conn_isolated}
-- Most repeatedly watched videos
WITH viw_cnts AS
(
SELECT video_title, COUNT(DISTINCT viewing_time) AS play_cnts, video_link
FROM view_history
WHERE video_link NOT LIKE '%music.youtube.com%' AND video_link NOT LIKE '%youtube.com\\post%'
GROUP BY video_link
ORDER BY COUNT(DISTINCT viewing_time) DESC
),
viw_cnts_1to10 AS
(
SELECT COUNT(*) AS total
     , COUNT(CASE WHEN play_cnts > 1 THEN video_title END) AS more_than_1
     , COUNT(CASE WHEN play_cnts > 2 THEN video_title END) AS more_than_2
     , COUNT(CASE WHEN play_cnts > 3 THEN video_title END) AS more_than_3
     , COUNT(CASE WHEN play_cnts > 4 THEN video_title END) AS more_than_4
     , COUNT(CASE WHEN play_cnts > 5 THEN video_title END) AS more_than_5
     , COUNT(CASE WHEN play_cnts > 6 THEN video_title END) AS more_than_6
     , COUNT(CASE WHEN play_cnts > 7 THEN video_title END) AS more_than_7
     , COUNT(CASE WHEN play_cnts > 8 THEN video_title END) AS more_than_8
     , COUNT(CASE WHEN play_cnts > 9 THEN video_title END) AS more_than_9
     , COUNT(CASE WHEN play_cnts > 10 THEN video_title END) AS more_than_10
FROM viw_cnts
)

-- proportion of repeatedly watched videos
SELECT CONCAT(ROUND(more_than_1 * 100.0 / total, 2), '%') AS more_than_1_pct
     , CONCAT(ROUND(more_than_2 * 100.0 / total, 2), '%') AS more_than_2_pct
     , CONCAT(ROUND(more_than_3 * 100.0 / total, 2), '%') AS more_than_3_pct
     , CONCAT(ROUND(more_than_4 * 100.0 / total, 2), '%') AS more_than_4_pct
     , CONCAT(ROUND(more_than_5 * 100.0 / total, 2), '%') AS more_than_5_pct
     , CONCAT(ROUND(more_than_6 * 100.0 / total, 2), '%') AS more_than_6_pct
     , CONCAT(ROUND(more_than_7 * 100.0 / total, 2), '%') AS more_than_7_pct
     , CONCAT(ROUND(more_than_8 * 100.0 / total, 2), '%') AS more_than_8_pct
     , CONCAT(ROUND(more_than_9 * 100.0 / total, 2), '%') AS more_than_9_pct
     , CONCAT(ROUND(more_than_10 * 100.0 / total, 2), '%') AS more_than_10_pct
FROM viw_cnts_1to10;
``` 

```{sql connection=conn_isolated}
SELECT channel_name
     , COUNT(DISTINCT video_link) as cnts
     , channel_link
FROM view_history
-- when watched video is deleted or disclosed by the channel
WHERE channel_name IS NOT 'Deleted_or_Disclosed' 
GROUP BY channel_link
ORDER BY cnts DESC
```


